---
title: "Analyzing EU Funding Data with eufundr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analyzing EU Funding Data with eufundr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(eufundr)
library(dplyr)
```

## Overview

This vignette demonstrates how to use the `eufundr` package to download and publicly available EU funding data from multiple sources

##  Download all data for Finland from all sources

```{r eval=FALSE}
all_data <- get_all_data("FI")

```

Access specific parts

```{r eval=FALSE}

projects <- all_data$kohesio_projects
beneficiaries <- all_data$kohesio_beneficiaries
fts <- all_data$fts
horizon2020 <- all_data$horizon_2020
horizon_europe <- all_data$horizon_europe
interreg <- all_data$interreg

```





## Download only certain country and sources

Get Greek kohesio projects

```{r eval=FALSE}
kohesio_projects = get_kohesio_projects(country = "GR")
```

Get Romanian kohesio beneficiaries

```{r eval=FALSE}
kohesio_beneficiaries = get_kohesio_beneficiaries(country = "RO")
```

 Get Dutch FTS data for year 2024

```{r eval=FALSE}
fts = get_fts_data(year = 2024, country =  "NL")
```

Get Swedish Horizon data

```{r eval=FALSE}
horizon = get_horizon_data(programme = "HORIZON", country = "SE")
```

Get Danish h2020 data

```{r eval=FALSE}
h2020 = get_horizon_data(programme = "h2020", country = "DK")
```

Get German interreg data

```{r eval=FALSE}
interreg = get_interreg_data(country = "DE")
```
